\chapter{Costs}
\justify
During the project, it is important to make an estimation on how many costs will be made during this project. By doing this, the client will have a rough idea what the price is by for example designing this prototype.  In this chapter, the estimation of these costs will be defined.

\section{LIDAR and Camera}
\justify
The LIDAR and the camera are the most important components of the project. These will probably be provided by the client or by the Hague University of Applied Sciences, but it might still be important information for future development. For example if the one of these component will break and will not be available anymore. The LIDAR is probably the most expensive of the two. The LIDAR cost currently between € 3000,- and € 4000,-. For this project, it is assumed a Basler camera will be used. A Basler camera costs around € 500,- to € 1000,-. 

\section{Microcontroller}
\justify
The system which will be designed by the project team needs a microcontroller to sync the LIDAR and the camera together. In the project description document provided on blackboard of the Hague University, it says it needs a Raspberry Pi for this. A Raspberry Pi (only the chip) costs around  € 8,-. For the first quarter, it might be better to first use a development board of Raspberry Pi. These cost around € 30,- to € 60,-. These can also probably be lend on the Hague University since these are used for some practical exercises.

\justify
Also what got mentioned in a meeting with the client is the use for a Arduino for a 10 Hz signal. An ATmega32 microcontroller (only the chip) costs between € 3,- and  € 5,-. An Arduino board differ in price depending on which the series is used but the price for these is around € 20,-.

\section{PCB}
\justify
In the project description document mentioned earlier, it says the client expects a PCB schematic and prototype for this project. The costs of printing a PCB excluding the components depends on how many layers the PCB needs. For a 2 layered PCB, it costs at Eurocircuits around € 50,- for 5 PCB’s and in China € 30,- inclusive transport costs. If a bigger and more complex PCB is needed, there is also a 4 layered PCB, but these are significantly more expensive (think about around € 100,- at Eurocircuits).  The price for all the components differ. Due to Covid, some prices are higher than normal or some components aren’t available. For resistors and capacitors, the price normally is around 2 or 3 cents each. IC’s are each around € 3,- to € 5,-. Finally there are the microcontrollers which have been explained in the previous paragraph. 
