\chapter{Organisation}
\label{ch:organisation}

\section{Roles and responsibilities}

The ECK Project group A will carry out the assignment on behalf of the Hague University of Applied Sciences. The client is Fernando Garcia Fernandez. The Project coach is Stephen O'Loughlin. In addition, the Hague University of Applied Sciences is an important stakeholder. 
\justify
Within the project team, several responsibilities will be carried out by various team members.

% This team will be led by AAAAA. He is accountable for ensuring that we adhere to our planned timetable and that each team member contributes actively to the outcome. Additionally, AAAAA will chair meetings and ensure that all team members have an equal opportunity to contribute.
\justify
The secretary for this project will be Bob Swinkels. He is responsible for recording the meeting's minutes and ensuring that they are sent to all attendees after the meeting.
\justify
This project's team members include Luca van Straaten, Bob Swinkels, Bas van Driel, and Bart Louwes. They will ensure that their job is completed on time. Additionally, they will all contribute to their collaboration and meetings.
\justify
The team will report weekly progress verbally to Fernando Garcia Fernandez and Stephen O'Loughlin. 
The client, Fernando Garcia Fernandez, is responsible for project acceptance and agrees upon completion.

\section{Methodology}

Throughout the project, we will use an agile approach. The design is split down into components created and evaluated in shorter iterations. Consequently, quality is maintained throughout the process, and faults in the final product are reduced.
The project planning (described in Chapter 4) and expected hours are calculated using Dr. Eliyahu Goldratt's Critical Chain. The Critical Chain technique strategically establishes project buffers to maintain delivery times.

\section{Communication within the team}

At least once a week, the team will meet to ensure that everyone is on the same page and aware of each other's successes and failures.
\justify
Bob Swinkels will provide the meeting notes to the team members after this meeting. If a team member is unable to attend a meeting, he is obligated to notify the project team at least 24 hours in advance.
Effective communication is critical to the successful completion of any project. As a result, several tools will be employed to ensure that communication is trouble-free.
\justify
We'll plan and monitor progress using GitHub Projects, an online Kanban-style management tool. If any tasks remain, they will be listed on a KanBan board with their associated due dates and allocated to the appropriate team members. In this manner, the whole team can view the project's status at a glance. 
\justify
Within the team, digital communication will take place through the team's Whatsapp group or via the university's email system. 
\justify
Git will be used to manage versions, synchronizing with the other team members through an online private Git repository housed on GitHub.