\chapter{Risks} % What are the risks for this project?

In this chapter, the risks of the project are discussed and contingencies will be planned.

\section{Complexity}

One major risk is that we will not finish this project, due to the complexity
of the project. The problem with this is that we will most likely only find
this out at or near the end of the project. This is why it is important to have
a good plan of requirements, which we will make at the start of the project.
\justify
However, as of writing this, we are fairly confident in our abilities to
produce a prototype and viable product to what we understand our client's
specifications to be.
\justify
Once we have a good plan of requirements, we hopefully can accurately gauge our
ability to finish the project throughout the duration of the project.

\section{Unforeseen circumstances}

Unforeseen circumstances which may result in us not being able to complete
our projects, or which may result in our projects being delayed, may
include such things as a global pandemic, alien invasion, robot uprising,
(nuclear) war and nuclear winter.

\justify
If such events occur, and we are still alive, and we are forced to stop our
work, we will reconvene with all parties and decide our next actions regarding
this project. Following actions may include such things as stopping or delaying
our meetings, stopping or delaying our research, stopping or delaying our
reporting on the research.

\justify
Other unforeseen circumstances could be that one of more of our team members
may be temporarily or permanently unavailable due to personal or other reasons.
In such a case, we will function as good as possible to complete our project.

\section{Delays}

If the project gets delayed due to any of the reasons listed above, we will
discuss this with our clients and determine what we can do to ensure our
clients satisfaction.

\section{Risks of evil}

The risk of our work being used in weapons of mass destruction, or sentient
killer robots, is not a legal concern for us. This is because we as the
researchers are not legally responsible for what our client decides to do with
this research.
\justify
However, each member of the team is responsible for weighing and accepting the
moral obligations that come with a project like this.
